\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-04 manuscript.tex

\begin{longtable}{ccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:tabDes}Descriptive Statistics}\\
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:tabDes} continued}}\\
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
\endhead
Item1 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25* & .16\\
Item2 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84* & .14\\
Item3 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79* & .19\\
Item4 & 2.87 & 1.59 & 0.08 & -1.60 & 0.83* & .19\\
Item5 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66* & .38\\
Item6 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87* & .33\\
Item7 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65* & .23\\
Item8 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86* & .00\\
Item9 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69* & .33\\
Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91* & .28\\
Item11 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89* & .35\\
Item12 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83* & .32\\
Item13 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91* & .10\\
Item14 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74* & .32\\
Item15 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60* & .15\\
Item16 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85* & .39\\
Item17 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82* & .05\\
Item18 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86* & .11\\
Item19 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82* & .17\\
Item20 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70* & .13\\
Item21 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41* & .01\\
Item22 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86* & .19\\
Item23 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43* & .21\\
Item24 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43* & .28\\
Item25 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89* & .11\\
Item26 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46* & .36\\
Item27 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67* & .22\\
Item28 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81* & .25\\
Item29 & 3.26 & 1.09 & -0.26 & -0.45 & 0.91* & .14\\
Item30 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76* & .30\\
Item31 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13* & .18\\
Item32 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49* & .31\\
Item33 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10* & .16\\
Item34 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87* & .16\\
Item35 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85* & .19\\
Item36 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87* & .25\\
Item37 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25* & .16\\
Item38 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84* & .18\\
Item39 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71* & .18\\
Item40 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88* & .21\\
Item41 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76* & .43\\
Item42 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83* & .44\\
Item43 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50* & .32\\
Item44 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91* & -.10\\
Item45 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85* & .20\\
Item46 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80* & .26\\
Item47 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86* & .26\\
Item48 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48* & .24\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

@@

The initial five-factor solution with all 48 items showed presence of cross-loading items (item 42, 16, \& 1) and poor factor loading (\textless.30) items (item 20, 3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , \& 46). At first, we discarded the items with poor factor-loading and ran another EFA on the remaining 34 items. This iteration of EFA also appeared as a misfit with items with poor factor-loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) . Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model. Finally, a five-factor EFA solution with 23 items was accepted with low RMSR = 0.04 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30. We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary). Table\ref{tab:TabEFA5} displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from -.47 to .99 indicating strong coefficients. The commonalities ranged between .10 to .99. However, the histogram of the absolute values of non-redundant residual-correlations (Fig\ref{fig:Residuals} showed 26.09\% correlations greater than the absolute value of .05, indicating under-factoring. (C. D. Desjardins, 2018). Subsequently, we fitted a six-factor solution. However, a factor emerged with only two salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.

In the five-factor solution, the first factor contained three items and explained 11\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) =.86). All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments. The second factor contained six items and explained 10\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) =.71). Items under this factor commonly investigate an individual's hours spent outdoor. The third factor contained five items and explained 9\% of the total variance. Items under this factor dealt with the specific behaviors pertaining to sleep. However, the internal consistency reliability coefficient was not satisfactory (\(\alpha\) =.62). The fourth factor contained three items and explained 9\% of the total variance with a satisfactory internal consistency (\(\alpha\) =.77). These three items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time. Lastly, the fifth factor contained six items and explained 6\% of the total variance. Under this factor tried to measure an individual's behavior lead by the awareness of light's influence on health. However, this factor showed unsatisfactory internal consistency reliability (\(\alpha\) =.49). It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure. As all of the emerged factors are highly interpretable, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA). Two items showed negative factor-loading (items 44 and 21). Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.

@@

\begin{tabular}{ccccccc}
\toprule
 & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{F2} & \multicolumn{1}{c}{F3} & \multicolumn{1}{c}{F4} & \multicolumn{1}{c}{F5} & \multicolumn{1}{c}{Communality}\\
\midrule
item43 & 0.99 & - & - & - & - & 0.99\\
item26 & 0.93 & - & - & - & - & 0.9\\
item32 & 0.8 & - & - & - & - & 0.67\\
item10 & - & 0.82 & - & - & - & 0.68\\
item47 & - & 0.82 & - & - & - & 0.7\\
item36 & - & 0.63 & - & - & - & 0.45\\
item44 & - & -0.47 & - & - & - & 0.24\\
item35 & - & 0.46 & - & - & - & 0.24\\
item13 & - & 0.34 & - & - & - & 0.13\\
item14 & - & - & 0.89 & - & - & 0.81\\
item41 & - & - & 0.7 & - & - & 0.6\\
item7 & - & - & 0.66 & - & - & 0.45\\
item27 & - & - & 0.38 & - & - & 0.21\\
item21 & - & - & -0.34 & - & - & 0.12\\
item34 & - & - & - & 0.84 & - & 0.74\\
item19 & - & - & - & 0.8 & - & 0.64\\
item2 & - & - & - & 0.67 & - & 0.54\\
item5 & - & - & - & - & 0.69 & 0.51\\
item24 & - & - & - & - & 0.54 & 0.33\\
item30 & - & - & - & - & 0.52 & 0.29\\
item1 & - & - & - & - & 0.35 & 0.13\\
item16 & - & - & - & - & 0.31 & 0.21\\
item28 & - & - & - & - & 0.31 & 0.1\\
\% of variance & 11 & 10 & 9 & 9 & 6 & -\\
\bottomrule
\addlinespace
\end{tabular}

@@

@@

@@

@@

>>>>

\begin{longtable}{ccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:tabDes}Descriptive Statistics}\\
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:tabDes} continued}}\\
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
\endhead
Item1 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81* & .25\\
Item2 & 2.87 & 1.59 & 0.08 & -1.60 & 0.81* & .19\\
Item3 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87* & .16\\
Item4 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43* & .28\\
Item5 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70* & .13\\
Item6 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85* & .20\\
Item7 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85* & .19\\
Item8 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91* & -.10\\
Item9 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91* & .10\\
Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91* & .28\\
Item11 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86* & .26\\
Item12 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87* & .25\\
Item13 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87* & .33\\
Item14 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80* & .26\\
Item15 & 3.26 & 1.09 & -0.26 & -0.45 & 0.80* & .14\\
Item16 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50* & .32\\
Item17 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49* & .31\\
Item18 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25* & .16\\
Item19 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13* & .18\\
Item20 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10* & .16\\
Item21 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25* & .16\\
Item22 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88* & .21\\
Item23 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89* & .11\\
Item24 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79* & .19\\
Item25 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86* & .19\\
Item26 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84* & .18\\
Item27 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82* & .17\\
Item28 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86* & .00\\
Item29 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86* & .11\\
Item30 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48* & .24\\
Item31 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83* & .44\\
Item32 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76* & .43\\
Item33 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74* & .32\\
Item34 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69* & .33\\
Item35 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65* & .23\\
Item36 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46* & .36\\
Item37 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41* & .01\\
Item38 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67* & .22\\
Item39 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82* & .05\\
Item40 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84* & .14\\
Item41 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43* & .21\\
Item42 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71* & .18\\
Item43 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60* & .15\\
Item44 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85* & .39\\
Item45 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76* & .30\\
Item46 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66* & .38\\
Item47 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83* & .32\\
Item48 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89* & .35\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

@@

Three rounds of EFA starting with all 48 items were conducted and problematic items were gradually discarded (cross-loading items and poor factor loading (\textless.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30. We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary). Table\ref{tab:TabEFA5} displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from -.49 to .99 indicating strong coefficients. The commonalities ranged between .11 to .99. However, the histogram of the absolute values of non-redundant residual-correlations (Fig\ref{fig:Residuals} showed 26.00\% correlations greater than the absolute value of .05, indicating a possible under-factoring. (C. D. Desjardins, 2018). Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.

In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .86). All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments. The second factor contained six items and explained 9.93\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .71). Items under this factor commonly investigate an individual's hours spent outdoor. The third factor contained five items and explained 8.83\% of the total variance. Items under this factor dealt with the specific behaviors pertaining to sleep. However, the internal consistency reliability coefficient was not satisfactory (\(\alpha\) = .68). The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, \(\alpha\) = .62. These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time. Lastly, the fifth factor contained six items and explained 6.14\% of the total variance.This factor tried to measure an individual's behavior lead by the awareness of light's influence on health. However, this factor showed unsatisfactory internal consistency reliability (\(\alpha\) = .53). It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure. As all of the emerged factors are highly interpretable, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA). Two items showed negative factor-loading (items 44 and 21). Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.

@@

\begin{tabular}{ccccccc}
\toprule
 & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{F2} & \multicolumn{1}{c}{F3} & \multicolumn{1}{c}{F4} & \multicolumn{1}{c}{F5} & \multicolumn{1}{c}{Communality}\\
\midrule
item16 & 0.99 & - & - & - & - & 0.99\\
item36 & 0.94 & - & - & - & - & 0.9\\
item17 & 0.8 & - & - & - & - & 0.66\\
item11 & - & 0.8 & - & - & - & 0.64\\
item10 & - & 0.76 & - & - & - & 0.59\\
item12 & - & 0.65 & - & - & - & 0.47\\
item7 & - & 0.5 & - & - & - & 0.27\\
item8 & - & -0.5 & - & - & - & 0.25\\
item9 & - & 0.32 & - & - & - & 0.11\\
item27 & - & - & 0.8 & - & - & 0.66\\
item3 & - & - & 0.8 & - & - & 0.68\\
item40 & - & - & 0.65 & - & - & 0.46\\
item30 & - & - & 0.45 & - & - & 0.35\\
item41 & - & - & -0.36 & - & - & 0.33\\
item33 & - & - & - & 0.74 & - & 0.56\\
item32 & - & - & - & 0.73 & - & 0.62\\
item35 & - & - & - & 0.66 & - & 0.45\\
item37 & - & - & - & -0.39 & - & 0.17\\
item38 & - & - & - & 0.36 & - & 0.18\\
item46 & - & - & - & - & 0.6 & 0.42\\
item45 & - & - & - & - & 0.59 & 0.37\\
item25 & - & - & - & - & 0.41 & 0.19\\
item4 & - & - & - & - & 0.41 & 0.22\\
item1 & - & - & - & - & 0.4 & 0.17\\
item26 & - & - & - & - & 0.39 & 0.17\\
internal Consistency & .86 & .71 & .68 & .62 & .53 & -\\
\% of variance & 10.25 & 9.93 & 8.83 & 8.44 & 6.14 & -\\
\bottomrule
\addlinespace
\end{tabular}

@@

\leavevmode\hypertarget{ref-R-car}{}%
Fox, J., \& Weisberg, S. (2019). \emph{An {R} companion to applied regression} (Third). Thousand Oaks {CA}: Sage. Retrieved from \url{https://socialsciences.mcmaster.ca/jfox/Books/Companion/}

\leavevmode\hypertarget{ref-R-carData}{}%
Fox, J., Weisberg, S., \& Price, B. (2020). \emph{carData: Companion to applied regression data sets}. Retrieved from \url{https://CRAN.R-project.org/package=carData}

\leavevmode\hypertarget{ref-R-Hmisc}{}%
Harrell Jr, F. E., Charles Dupont, with contributions from, \& others., many. (2021). \emph{Hmisc: Harrell miscellaneous}. Retrieved from \url{https://CRAN.R-project.org/package=Hmisc}

@@

\leavevmode\hypertarget{ref-R-lattice}{}%
Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with r}. New York: Springer. Retrieved from \url{http://lmdvr.r-forge.r-project.org}

@@

\leavevmode\hypertarget{ref-R-survival-book}{}%
Terry M. Therneau, \& Patricia M. Grambsch. (2000). \emph{Modeling survival data: Extending the {C}ox model}. New York: Springer.

@@

\leavevmode\hypertarget{ref-R-Formula}{}%
Zeileis, A., \& Croissant, Y. (2010). Extended model formulas in {R}: Multiple parts and multiple responses. \emph{Journal of Statistical Software}, \emph{34}(1), 1--13. \url{https://doi.org/10.18637/jss.v034.i01}
